TO FIND

### 2013-05-23 ms.tex
Neutrality and other interactions

Finally, Figs. 3 and 4 present, respectively, the between patch $\beta$
diversity as a function of the shape of the network, under the three dynamic
models. We simply used Bray-Curtis measure of dissimilarity between patches.  In
Fig. 3, the distance is expressed as the euclidean (geographic) distance between
two patches. Although this neglects how dispersal connects the different
patches, there is already a clear signal of geographic distance on $\beta$
diversity. In both the neutral and patch dynamics model, local communities
become increasingly dissimilar when the distance between them increases. In
other words, two communities which are close to each other will share a large
proportion of their species, whereas two communities which are afar will share a
small proportion.  In the species-sorting model, the relationship between
distance and dissimilarity is similar, Nonetheless, it forms an enveloppe of
points (with most points lying in the upper-left part of the graph). While two
distant communities will be dissimilar, there is no telling how dissimilar two
close communities will be. Note this relationship for SS varies significantly
with the spatial distribution of microsites (not shown). At one extreme, if all
patches hold the same average conditions, then we should expect no relationship
between dissimilarity and distance. On the other hand, if the average conditions
are highly variable among localities (as in here), then we should expect two
communities close to be potentially dissimilar (if conditions are different) or
similar (if they are the same). The variance should thus be larger. A
distance-dissimilarity relationship arises in the situation where dispersal
promotes a mass effect (as in here). Such results emphasize the interaction
between spatial contingencies (here connectivity and distribution of
environmental conditions).

To a vast extent, these relationships are preseved when looking at the
topological distances (Fiig. 4), i.e. along how many edges should one travel to connect
two patchs. Interestingly enough, the distance-dissimilarity relationship for
the neutral model is markedly hump-shaped, with sites being at a medium distance
having the maximal dissimilarity.

@@

%TP
How to add other types of interactions
	- Wootton: variation arises from unaccounted interactions

>>>>

Finally, Figs. 3 and 4 present, respectively, the between patch $\beta$
diversity as a function of the shape of the network, under the three dynamic
models. We used Bray-Curtis measure of dissimilarity between patches. In
Fig. 3, the distance is expressed as the euclidean (geographic) distance between
two patches. Although this neglects how dispersal connects the different
patches, there is already a clear signal of geographic distance on $\beta$
diversity. In both the neutral and patch dynamics model, local communities
become increasingly dissimilar when the distance between them increases. In
other words, two communities which are close to each other will share a large
proportion of their species pool, whereas two communities which are afar will share a
small proportion.  In the species-sorting model, the relationship between
distance and dissimilarity is similar, Nonetheless, it forms an enveloppe of
points (with most points lying in the upper-left part of the graph). While two
distant communities will be dissimilar, there is no telling how dissimilar two
close communities will be. Note this relationship for SS varies significantly
with the spatial distribution of microsites (not shown). At one extreme, if all
patches hold the same average conditions, then we should expect no relationship
between dissimilarity and distance. On the other hand, if the average conditions
are highly variable among localities (as in here), then we should expect two
communities close to be potentially dissimilar (if conditions are different) or
similar (if they are the same). The variance should thus be larger. A
distance-dissimilarity relationship arises in the situation where dispersal
promotes a mass effect (as in here). Such results emphasize the interaction
between spatial contingencies (here connectivity and distribution of
environmental conditions).

To a vast extent, these relationships are preserved when looking at the
topological distances (Fiig. 4), i.e. along how many edges should one travel to
connect two patchs. Interestingly enough, the distance-dissimilarity
relationship for the neutral model is markedly hump-shaped, with sites being at
a medium distance having the maximal dissimilarity.

@@

%TP
Finally, our analyses emphasize the need to expand on the canonial neutral
theory. As pointed out by Wootoon2005Nature433, most of the unexplained
deviation of empirical community from the prediction of accurately calibrated
neutral models can be attirbuted to non-competitive interactions. Canard2012
proposed that neutral processes can explain the network structure of trophic
interactions with a good accuracy. Incorporating reasonable complexity in the
mechanisms adressed by neutral models is not a theoreticians' exercice: it will
re-inforce the usefulness of the neutral theory as an operational concept,
specifically one that can be used to derive baseline predictions about (i) the
expected local species richness, and (ii) the expected species pool
dissimilarity at the between-site and regional scales. These predictions are the
benchmark against which empirical relev\'es of species richness and community
structure ought to be compared, and coming up with realistic parameters to
calibrate these models calls for a closer cooperation and dialogue between
theoreticians and empiricists.
